Learning and Reputation under Monopoly and Duopoly: \\A Competing Bandits Approach

### 2018-08-26 paper/competing_bandits.tex
updated paper

\begin{finding}
\textit{Algorithms that engage in purposeful exploration can lead to implicit relative reputation costs compared to the greedy alternative in the earlier rounds. We observe this under the Uniform and Heavy Tail priors. However, it is not observed under the Needle In Haystack prior}
\end{finding}

@@

\begin{definition}
\textit{Relative reputation cost and benefit} - the relative reputation loss from an algorithm that engages in purposeful exploration compared to the greedy alternative. It is an empirical definition based on the relative reputation proportion where the ``cost" regime is when the proportion $< 0.5$ and the ``benefit" regime is when the proportion is $> 0.5$ for the better algorithm. We call the priors where there is an early costly period followed by a later benefit period, relative reputation costly priors.
\end{definition}

>>>>

\begin{finding}
\textit{Purposeful exploration can lead to relative reputational costs compared to the greedy alternative and this leads to $TS$ doing worse than $DG$ for small time horizons. We observe this under the Uniform and Heavy Tail priors. However, it is not observed under the Needle In Haystack prior}
\end{finding}

@@

\begin{definition}
\textit{Relative reputation cost and benefit} - the relative reputation loss an algorithm incurs from purposeful exploration compared to the greedy alternative. Here we treat it as an empirical definition based on the relative reputation proportion where the ``cost" regime is when the proportion $< 0.5$ and the ``benefit" regime is when the proportion is $> 0.5$ for the better algorithm. We call the priors where there is an early costly period followed by a later benefit period, relative reputation costly priors.
\end{definition}
